Schramm-Loewner evolution in tricritical Ising model

### 2013-05-31 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
minor
Some text added

>>>>

Bolzmann weights for RSOS models are defined as follows \cite{behrend2001integrable}. Consider
graph ${\cal G}$ (Dynkin diagram $A_4$ for the tricritical Ising
model). This graph has the adjacency matrix $G$. Let $2\cos\lambda$ be the
highest eigenvalue of matrix $G$ and $\psi$ the corresponding eigenvector:
\begin{equation}
  \label{eq:2}
  \sum_{b\in {\cal G}} G_{ab}\psi_b = 2\cos(\lambda) \psi_a
\end{equation}
By the Perron-Frobenius theorem $\psi_a \neq 0$ for all $a\in {\cal
  G}$. 
The parametrization for eigenvalue is connected with
representation theory of Temperley-Lieb algebra ${\cal T}(L,\lambda)$,
where $L\in \mathbb{Z}_+$ and $\lambda\in\mathbb{C}$, generated by the
identity operator $I$ and generators $e_1,\dots, e_L$ satisfying
\begin{equation}
  \label{eq:3}
  \begin{array}{l}
    e_j^2 = 2\cos(\lambda) e_j\\
    e_j e_k e_j = e_j, \quad |j-k|=1\\
    e_j e_k = e_k e_j , \quad |j-k|>1
  \end{array}
\end{equation}
For ${\cal G}, \lambda, \psi$ the generators of ${\cal T}(L,\lambda)$
are given by matrices with rows and columns labeled by the paths in ${\cal G}^{L+2}$
\begin{equation}
  \label{eq:4}
  \left(e_j\right)_{(a_0,\dots, a_{L+1}),(b_0,\dots,
    b_{L+1})}=\frac{\psi^{1/2}_{a_j} \psi^{1/2}_{b_j}}{\psi_{a_{j-1}}}
  \delta_{a_{j-1} a_{j+1}} \prod_{\substack{k=0\\k\neq j}}^{L+1}\delta_{a_k b_k}
\end{equation}

Bolzmann weights are given by the expression
\begin{equation}
  \label{eq:5}
  W\left.\left(
    \begin{array}{cc}
      d & c\\
      a & b
    \end{array}\right| u \right)
= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
  \psi_c^{1/2}}{\psi_b} \delta_{bd},
\end{equation}
where
  \begin{equation}
    \label{eq:6}
    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
%%      \left.s_r(u)\right|_{\frac{\lambda}{\pi}\in \mathbb{Z}} =
%%      \lim_{\lambda'\to \lambda} \frac{\sin(r \lambda'
%%        +(\lambda'-\lambda)u)}{\sin \lambda'}
  \end{equation}
We are interested in the case $A_4$, so $\lambda=0.62831853071796$ and
isotropic case $u=\lambda/2$. Conformal point is
$u=\xi_1=\xi_2=\lambda/2$. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda}$.
